03_wrangle

### 2020-07-31 analysis/03_datawrangling.Rmd
better file names

```{r write}
write.csv(allDEG, "../results/03_allDEG.csv", row.names = F)
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
write.csv(parentalcaregenes, "../metadata/03_parentalcaregenes.csv")
write.csv(wideDEGsSequential, "../results/03_wideDEGsSequential.csv")
```

>>>>

```{r write}
write.csv(allDEG, "../results/03_allDEG.csv", row.names = F)
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
write.csv(wideDEGsSequential, "../results/table1.csv", row.names = F)
```
